From Education to Entrepreneurship

### 2014-12-06 index.Rmd
Added and revised text, added map for WayofTeaching

**Key Question**
To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?

@@

@@

>>>>

### Key Question 
To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?

@@

### Selected Variables

@@

Variable | Indicator 
-------------|---------------
Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

### Causal Chain

Our decision to select and investigate these variables was based on the following causal chain

1. An education system that reinforces self-confidence

2. Higher degree of individual self-esteem

3. Higher probability an individual becomes an entrepreneur

4. Higher rate of entrepreneurship at a country-level

### Geographic Variation in our Explanatory Variable

As expected, there is significant variation among OECD countries with respect to each of the variables investigated.  The most important of these variables is our explanatory variable, "WayofTeaching".  This is a measure of how well teaching methods support self-confidence in each country.  The following interactive chart displays variation in self confidence with the log of the mean survey response from each country over 2001-2013 timeframe.

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

# Drop unnecessary column 1
WayofTeaching$X <- NULL

# Change data from long to wide format
WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")

# Delete variable name in Year columns
names(WT) <- gsub("WayofTeaching.", "", names(WT))

# Duplicate df for future use
WT2 <- WT

# Generate a new column with mean of all other columns
WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010")), na.rm = TRUE)

# Drop year columns, leaving only mean column
WT$'2001' <- NULL
WT$'2002' <- NULL
WT$'2003' <- NULL
WT$'2004' <- NULL
WT$'2005' <- NULL
WT$'2006' <- NULL
WT$'2007' <- NULL
WT$'2008' <- NULL
WT$'2009' <- NULL
WT$'2010' <- NULL
WT$'2011' <- NULL
WT$'2012' <- NULL
WT$'2013' <- NULL
WT$row.names <- NULL

# Create 
WT[, 3] <- round(log(WT[, 3]), digits = 2)
```

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
library(googleVis)

# Plot
WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

print(WT_map, tag = 'chart')

```
